Analysis : exp220 - 228 (Nov 2018, for J Neurophys draft 2018)

### 2018-12-08 resistingrhythm/analysis/paper_figures_v4.Rmd
Cleanup imports
Tweak vis for paper

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(grid)
library(ggpubr)
library(cowplot)

@@

# Clean up
rm(df, exp_code, i, o_c, o_r, osc_codes, osc_rates, s_c, stim_codes)
```

@@

# Figure: Error
```{r, fig.width=3.2, fig.height=3.1}
# ------------------------------------------------------------
# Kappa
results220 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate) %>% 
  mutate(
    M_error=mean(mse_error), SD_error=sd(mse_error), 
    M_rate_k=mean(rate_k), SD_rate_k=sd(rate_k), 
    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp1
tmp1$mode <- rep("No homeostatsis", nrow(tmp1))
results221 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate) %>% 
  mutate(
    M_error=mean(mse_error), SD_error=sd(mse_error), 
    M_rate_k=mean(rate_k), SD_rate_k=sd(rate_k), 
    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp2
tmp2$mode <- rep("Homeostatsis", nrow(tmp2))

@@

# Rate
bind_rows(tmp1, tmp2) %>% 
ggplot(mapping=aes(x=M_rate_k, y=M_error, color=mode)) +
  geom_point(size=0.2) +
  geom_errorbar(mapping=aes(x=M_rate_k, ymin=M_error - SD_error, ymax=M_error + SD_error),
                width=0.004, size=0.2) +
  geom_errorbarh(mapping=aes(y=M_error, xmin=M_rate_k - SD_rate_k, xmax=M_rate_k + SD_rate_k),
                 height=0.002, size=0.2) +
  scale_color_manual(values=c("black", "darkgrey")) +
  labs(title="c.", y="Log error (s)", x="Pop. rate") +
  # lims(x=c(0.0, 0.25)) +
  scale_y_log10() + annotation_logticks() +
  theme_classic2() + 
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
        legend.position = "none") -> p3

@@

# Rate
bind_rows(tmp1, tmp2) %>% 
ggplot(mapping=aes(x=M_rate_k, y=M_error, color=mode)) +
  geom_point(size=0.2) +
  geom_errorbar(mapping=aes(x=M_rate_k, ymin=M_error - SD_error, ymax=M_error + SD_error),
                width=0.004, size=0.2) +
  geom_errorbarh(mapping=aes(y=M_error, xmin=M_rate_k - SD_rate_k, xmax=M_rate_k + SD_rate_k),
                 height=0.002, size=0.2) +
  scale_color_manual(values=c("black", "darkgrey")) +
  labs(title="d.", y="Log error (s)", x="Pop. rate") +
  # lims(x=c(0.0, 0.25)) +
  theme_classic2() + 
  scale_y_log10() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
        legend.title=element_blank()) -> p4

@@

# -
layout_matrix <- rbind(
  c(5, 5, 5, 6, 6, 6, 6, NA),
  c(1, 1, 1, 2, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2, 2),
  c(3, 3, 3, 4, 4, 4, 4, 4),
  c(3, 3, 3, 4, 4, 4, 4, 4),
  c(3, 3, 3, 4, 4, 4, 4, 4),
  c(3, 3, 3, 4, 4, 4, 4, 4)
)
grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=layout_matrix)

png(file="fig3.png", bg="white", width=6.4, height=2.2, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=layout_matrix)
dev.off()
```

# Figure: Calcium control
```{r, fig.width=2.4, fig.height=1.6}
# -
results228 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp1

@@

# -
p3 <- textGrob("Synchrony")
p4 <- textGrob("Excitability")

# -
layout_matrix <- rbind(
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(3, 1, 1, 5),
  c(3, 1, 1, 5),
  c(3, 1, 1, 5), 
  c(3, 1, 1, 5) 
)
p5 <- nullGrob()
grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)

png(file="fig4.png", bg="white", width=4.8, height=3.2, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
dev.off()
```

>>>>

```{r, message=FALSE}
library(ggplot2)
library(latex2exp)
library(dplyr)
library(magrittr)
library(readr)
library(gridExtra)
library(grid)
library(ggpubr)
library(cowplot)

@@

# Clean up
rm(df, exp_code, i, o_c, o_r, osc_codes, osc_rates, s_c, stim_codes)

# 231
tau_h <- 600
exp_code <- 231
n_cycles <- c("4", "8", "480")

results231 <- NULL
for(i in 1:length(n_cycles)){
  n_c <- n_cycles[i]

  # Load the csv
  df <- read_csv(paste(data_path, 
                       "exp", as.character(exp_code), 
                       "_c", n_c, 
                       ".csv", sep=""))  
  # Add metadata
  df$n_cycles <- rep(n_c, nrow(df))
  df$frac_tau_h <- rep(as.character(
    (
      round(as.numeric(n_c)*(1/8)/tau_h, digits=3)
    ), nrow(df)
    )
  )
  df$osc_rate <- rep("6", nrow(df))
  df$freq <- rep("b", nrow(df))
  df$synapse <- rep("Excitatory", nrow(df))
  df$homeo <- rep("Homeostasis", nrow(df))
  if(n_c <= 8){
    df$mode <- rep("Burst", nrow(df))
  } else {
    df$mode <- rep("Tonic", nrow(df))
  }

  results231 <- rbind(results231, df)
}

# Realistic tau_h and oscillation.
exp_code <- 232
results232 <- NULL
for(i in 1:length(n_cycles)){
  n_c <- n_cycles[i]

  # Load the csv
  df <- read_csv(paste(data_path, 
                       "exp", as.character(exp_code), 
                       "_c", n_c, 
                       ".csv", sep=""))  
  # Add metadata
  df$n_cycles <- rep(n_c, nrow(df))
  df$frac_tau_h <- rep(as.character(
    (
      round(as.numeric(n_c)*(1/8)/tau_h, digits=3)
    ), nrow(df)
    )
  )
  df$osc_rate <- rep("6", nrow(df))
  df$freq <- rep("b", nrow(df))
  df$synapse <- rep("Excitatory", nrow(df))
  df$homeo <- rep("No homeostasis", nrow(df))
  if(n_c <= 8){
    df$mode <- rep("Burst", nrow(df))
  } else {
    df$mode <- rep("Tonic", nrow(df))
  }

  results232 <- rbind(results232, df)
}

rm(df, n_c, i, exp_code)
```

@@

# Figure: Error
```{r, fig.width=3.2, fig.height=1.2}
# ------------------------------------------------------------
# Kappa
results220 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate) %>% 
  mutate(
    M_error=mean(mse_error), SD_error=sd(mse_error), 
    M_rate_k=mean(rate_k), SD_rate_k=sd(rate_k), 
    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp1
tmp1$mode <- rep("No homeostatsis", nrow(tmp1))
results221 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate) %>% 
  mutate(
    M_error=mean(mse_error), SD_error=sd(mse_error), 
    M_rate_k=mean(rate_k), SD_rate_k=sd(rate_k), 
    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp2
tmp2$mode <- rep("Homeostatsis", nrow(tmp2))

@@

# Rate
# bind_rows(tmp1, tmp2) %>% 
# ggplot(mapping=aes(x=M_rate_k, y=M_error, color=mode)) +
#   geom_point(size=0.2) +
#   geom_errorbar(mapping=aes(x=M_rate_k, ymin=M_error - SD_error, ymax=M_error + SD_error),
#                 width=0.004, size=0.2) +
#   geom_errorbarh(mapping=aes(y=M_error, xmin=M_rate_k - SD_rate_k, xmax=M_rate_k + SD_rate_k),
#                  height=0.002, size=0.2) +
#   scale_color_manual(values=c("black", "darkgrey")) +
#   labs(title="c.", y="Log error (s)", x="Pop. rate") +
#   # lims(x=c(0.0, 0.25)) +
#   scale_y_log10() + annotation_logticks() +
#   theme_classic2() + 
#   theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
#         legend.position = "none") -> p3

@@

# Rate
# bind_rows(tmp1, tmp2) %>% 
# ggplot(mapping=aes(x=M_rate_k, y=M_error, color=mode)) +
#   geom_point(size=0.2) +
#   geom_errorbar(mapping=aes(x=M_rate_k, ymin=M_error - SD_error, ymax=M_error + SD_error),
#                 width=0.004, size=0.2) +
#   geom_errorbarh(mapping=aes(y=M_error, xmin=M_rate_k - SD_rate_k, xmax=M_rate_k + SD_rate_k),
#                  height=0.002, size=0.2) +
#   scale_color_manual(values=c("black", "darkgrey")) +
#   labs(title="d.", y="Log error (s)", x="Pop. rate") +
#   # lims(x=c(0.0, 0.25)) +
#   theme_classic2() + 
#   scale_y_log10() +
#   theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
#         legend.title=element_blank()) -> p4

@@

# -
layout_matrix <- rbind(
  c(3, 3, 3, 4, 4, 4, 4, NA),
  c(1, 1, 1, 2, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2, 2)
)
grid.arrange(p1, p2, p5, p6, layout_matrix=layout_matrix)

png(file="fig3.png", bg="white", width=6.4, height=2.4, unit="in", res=300)
grid.arrange(p1, p2, p5, p6, layout_matrix=layout_matrix)
dev.off()
```

# Figure: Control
```{r, fig.width=2.4, fig.height=2.8}
# -
results228 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp1

@@

# -----------------------------------------------------------------------------------
# Frac of tau_h
# rate
rbind(results231, results232) %>% 
  ggplot(aes(x=frac_tau_h, y=rate_k, color=homeo, group=interaction(homeo, frac_tau_h))) +
  geom_boxplot(size=0.6) +
  stat_compare_means(method="wilcox.test", label="p.signif", 
                     label.x=1.3, size=3, show.legend=FALSE) +
  labs(title="c.", y="Pop. rate", x=TeX("$t_{oscillation} / \\tau_{homeostasis}$")) +
  scale_color_manual(values=c("black", "grey"), name=NA) +
  theme_classic2() +
  theme(
    plot.title = element_text(hjust = -.5, size=18, face="bold"),
    legend.background = element_rect(colour ="black"),
    legend.position = c(1.35, 0.5),
    legend.title=element_blank(),
    legend.key.size = unit(.3, "cm")) -> p6

# -
p3 <- textGrob("")
p4 <- textGrob("Target [Ca]\nperturbation")
p8 <- textGrob(TeX("Biological $\\tau_h$"))
p5 <- nullGrob()
p9 <- nullGrob()

# -
# layout_matrix <- rbind(
#   c(4, 2, 2, 5), 6, 6, 5),
#   c(4, 2, 2, 5), 6, 6, 5),
#   c(4, 2, 2, 5), 6, 6, 5),
#   c(4, 2, 2, 5), 6, 6, 5),
#   c(3, 1, 1, 5), 7, 7, 5),
#   c(3, 1, 1, 5), 7, 7, 5),
#   c(3, 1, 1, 5), 7, 7, 5), 
#   c(3, 1, 1, 5), 7, 7, 5) 
# )

layout_matrix <- rbind(
  c(4, 2, 2, 5), 
  c(4, 2, 2, 5), 
  c(4, 2, 2, 5), 
  c(4, 2, 2, 5), 
  c(3, 1, 1, 5), 
  c(3, 1, 1, 5), 
  c(3, 1, 1, 5),  
  c(3, 1, 1, 9), 
  c(8, 6, 6, 9),
  c(8, 6, 6, 9),
  c(8, 6, 6, 9),
  c(8, 6, 6, 9)
)
grid.arrange(p1, p2, p3, p4, p5, p6, p8, p9, layout_matrix=layout_matrix)

png(file="fig4.png", bg="white", width=4.8, height=5.6, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, p6, p8, p9, layout_matrix=layout_matrix)
dev.off()
```
